\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[total={6.5in,9in}]{geometry}
\usepackage{xcolor}

\newcommand[1]{\FJH}{\color{blue}#1}


\title{Proposal for the \\
15th International Conference on Monte Carlo Methods and Applications (MCM)\\
MCM 2025 in Chicago, IL USA}
%\author{jinliang98 }
%\date{February 2022}

\begin{document}

\maketitle

\section{Summary of the proposal}
The \FJH{Fred write}

\section{Local organizers}
 The organizing team represents different thematic currents in the
community, both on theoretical, numerical and application aspects.
\begin{itemize}
    \item  Fred Hickernell, Applied Mathematics, Illinois Institute of Technology
    \item  Lulu Kang, Applied Mathematics, Illinois Institute of Technology
    \item  Yuhan Ding, Applied Mathematics, Illinois Institute of Technology
    \item  Romit Maulik/Jinqiao (Fred)
    \item  Maggie Cheng/David (Fred)
\item  Yiou Li (???)
\item  Potential people from UIC. Try by Lulu.
\end{itemize}

\section{Program Committee}

The program committee will be an international and multidisciplinary in nature.  It will be drawn from those who have had a history of contribution to the MCM series plus those whose expertise may add a valuable dimension to the conference.

\section{Proceedings}

\section{Conference Venue}

The conference will be held at Illinois Tech Hermann Hall. 
A conference dinner on the Chicago River or at Chinatown with a night architecture tour will be organized.

\section{Tentative Dates and Schedules}
July 14th to 18th 2025

The dates will be finalized to avoid overlap with the 2025 SIAM Annual Meeting, the August 2 – 7, 2025, Joint Statistics Meeting, 
5 days conference with the following format for each day
\begin{itemize}
    \item  Morning: keynote speaker (1h), parallel mini-symposia (2h)
    \item  Afternoon: keynote speaker (1h), parallel mini-symposia (2h)
\end{itemize}
Poster sessions: at the lunch breaks
\section{Topics}


\section{Budget}
The registration fees would be 600\$/person including the conf. dinner, coffee/lunch breaks. Only expenses from keynote speakers will be covered.


\section{History of conferences}
\begin{itemize}
\item Paris, July 2023
\item  Mannheim, August 2021
\item Sydney, Australia, July 2019
\item Montreal, Canada, July 2017
\item  Linz, Austria, July 2015
\item  Annecy-le-Vieux, France, July 2013
\item  Borovets, Bulgaria, August 2011
\item  Brussels, Belgium, September 2009
\item  Reading, UK, June 2007
\item  Tallahassee, USA, May 2005
\item  Berlin, Germany, September 2003
\item  Salzburg, Austria, September 2001
\item  Varna, Bulgaria, June 1999
\item  Brussels, Belgium, April 1997
\end{itemize}


\end{document}
